\documentclass[12pt]{article}
\usepackage{fullpage}
\begin{document}
\title{\emph{Should We worry about AI?}\\
	\emph{Now or Future?}}
\author{Cyro Chun F, Chak}
\maketitle
\section{Introduction}
Since The founder of Artificial Intelligence(AI) John McCarthy has proposed the study of "a 2-month, 10-man study of artificial intelligence", worldwide computer scientists started to investigate the field of AI\cite{MccarthyResearch}. From the day of the proposal released till now, it has been for 60 years, our technology is still far away from General AI. As we get closer and closer to General AI day by day, thousands, or maybe millions of people are worried about the day of General AI arrival. However, most of them have misunderstanding ideas and some myths that lead civilians to have an incorrect mindset of Artificial Intelligence. Especially Internet and social media have been used almost over the world, there may exist some anti-AI groups that are proposing certain non-sense statements that we should not worry about. In fact, since we human race has already started the project to create General AI, which maybe calls as "Evil", we should plan ahead about AI safety, and what we should concern about AI.

\section{General AI will eliminate human race?????}
A few months ago, a friend of mine sent me a video entitled with something "Future of AI", it got my interests and I watched the entire 3 minutes videos. All I could say about the clip is completely non-sense, the clip showed that some automated robots that are armed with guns break into the building and kill all the people inside the building. Whenever they detected any kind of living things, the robots would kill. When they r done killing, they all said, "Mission complete". This video has come to a lot of viewers to comment. In the discussion section below the video, some are argued the video is not saying the truth, and some are saying this is what we are going to have, or we are building to against our own human race. By reading the comment section, I realize there is a big misunderstanding in the whole community about AI. Not only the basic concept of artificial intelligence is wrong, the video is leading audiences to a wrong direction of thinking about AI. First of all, we should consider what will AGI (is denoted as General AI) will bring us to. In the video, it seems like automated robots have brought us violence and wars. However, the robots said Mission complete, which most of the viewers missed this important clue, and we can also think of someone has controlled the robots. We should not concern about how dangerous the robots are, but what the purpose of using robots. Scientists create Artificial Intelligence to make our lives easier, but not starting a war. In this case, the video is not the appropriate example to illustrate that we should concern about the dangers of Artificial Intelligence. Besides, an article from future of life also mentioned similar experience with mine. According to the article, "Benefits \& Risks of Artificial Intelligence", it said there are some articles mentioned we should worry about robots will destroy the human race with a picture of a robot armed with a gun with red shinny face of an evil looking robot\cite{FutureOfLife}. The author also said we should not worry about robots, but instead worry about intelligence\cite{FutureOfLife}. In fact, not only robots, anything can be dangerous, it depends on how do you use. We control how we want the robot to be done. We should worry about once we build a super intelligence AI, somebody may use it to conduct the destructive event with the malicious motive.
\section{Do we still have Job after AI is created?}
On the other hand, some reasons that we should concern about the economy. As the fundamental functions of building Artificial Intelligence is to make our lives easier, it would bring us a concern about jobs definitely. Not even when General will be built, a lot of jobs will be created and deleted. It has been happening since 2004. According to the article, "Should we be worried about AI?" by Science Focus Magazine, it mentioned, "We should be worried about real human stupidity, not imaginary artificial intelligence." They have also provided some suggestions that I think governments and industries should follow, one out of five suggestions that mentioned about the economy, it said tons of jobs will be eliminated and created since a lot of works will be replaced by robots, especially low-income jobs\cite{sciencefocus}. They also related that we should think this transformation is negative impacts to the society, we should undergo the change as agricultural revolution took millions of years to change, the industrial revolution takes a few centuries, but our technology world only took only a few decennials\cite{sciencefocus}. It makes sense that we are not yet adapted this brand-new concept. In the 2016 report released by Executive Office of the President National Science and Technology Council Committee on Technology, "Preparing For the future of Artificial Intelligence, it mentioned a lot of good points that I think government besides U.S and industries should also follow up, it talked a list of categories about Artificial Intelligence and gave out a lot of recommendations to the Executive Office. Under the AI, Automation, and the Economy, it provides a recommendation that the Executive Office should publish a report to investigate the effects of artificial intelligence and how does it effect on U.S. job market\cite{2016Report}. 
\section{Will they outsmart human?}
Besides the suggestion given by the report, I think plan over how we control an Artificial Intelligence to do some jobs that may consist decision making about ethics. Ethics problems will become one of the majority issues that scientists maybe facing since they do not have feelings and it is hard for them to make ethical decisions. This will be a new topic about can AI outsmart human, as each of us may have a different opinion about the ethical problem. However, this may come across the problem that machine learning. Machine Learning is still in-progress in the field. However, someone argues there was an incident about artificial intelligence become bad in our society that happened on twitter. Based on the post from The Verge, "Twitter taught Microsoft's AI chatbot to be a racist asshole in less than a day" by James Vincent, it described Twitter has loaded up an artificial intelligence based automated chat robot\cite{verge}. It turned into disasters since some users have imbued some violent related information to the robot. With machine learning, the robots learned everything they got, and within a few minutes, they turn into an evil robot. It absorbed every message but get some inappropriate and nasty message that the intelligence has no clue to identify them. Although this release had made artificial intelligence become a bad image of technology, technology is still improving. We could not let an impurity destroy the whole theory that is made of. After a few decades or centuries, we might be able to get a better intelligence. But We don't know it by now.
\section{Conclusion}
After all, we still do not know when we will have a super intelligence robot around, some say a few decades, some said never, or after hundred years. We do not have a clear answer. Right now, we do not have the General AI, but we have a clear concept that will bring us some benefits, but also troubles. This is the reason why we should talk about AI safety as early as now so that we could be able to understand what we are coming after. We all know not the only United States are investigating AI technology, but also other countries. Despite the fact that the US has announced some safety suggestions or recommendation to the companies, the international companies besides the U.S should follow it just in case anything happens.
\newpage
\begin{thebibliography}{9}
\bibitem{FutureOfLife}
Benefits \& Risks of Artificial Intelligence
\\\texttt{https://futureoflife.org/background/benefits-risks-of-artificial-intelligence/}

\bibitem{2016Report}
Executive Office of the President National Science and Technology Council Committee on technology
Preparing For The Future Of Artificial Intelligence
\\\texttt{https://cra.org/ccc/wpcontent/uploads/sites/2/2016/11/NSTC{\_}prearing{\_}for{\_}the{\_}future{\_}of{\_}ai.pdf}

\bibitem{sciencefocus}
Luciano Floridi
Should we be worried about AI?
\\\texttt{http://www.sciencefocus.com/article/future/should-we-be-worried-about-ai}

\bibitem{MccarthyResearch}
John McCarthy, Marvin L. Minsky, Nathaniel Rochester, Claude E. Shannon
A Proposal for the Dartmouth Summer Research Project on Artificial Intelligence
\textit{AI Magazine Volume 27 Number 4}
2006
\bibitem{Mccarthy}
Vladimir Lifschitz
John McCarthy
\textit{The scientist who set computers on the path to common sense.}
\texttt{https://www.nature.com/articles/480040a.pdf?origin=ppub}
\bibitem{verge}
James Vincent
\texttt{https://www.theverge.com/2016/3/24/11297050/tay-microsoft-chatbot-racist}
\end{thebibliography}

\end{document}
